---
title: "chlorophyll_r_analysis"
output: html_document
---

```{r}
library(tidyverse)
library(pals)
library(RColorBrewer)
library(ggpmisc)

root.dir <- rprojroot::find_root("2019_chlorophyll_sensor_analysis.Rproj")

# Gather all 2019 field data and filter down to sites where ProDSS was used. Check on -5 values!

field.data.macro <- file.path(root.dir, "data", "20191212_Macro_Field_2019.xlsx") %>% 
  readxl::read_excel(sheet = "Sheet1") %>% 
  mutate(Chl_ugL = as.numeric(Chl_ugL)) %>% 
  mutate(PC_ugL = as.numeric(PC_ugL)) %>% 
  mutate(Chl_RFU = as.numeric(Chl_RFU)) %>% 
  mutate(PC_RFU = as.numeric(PC_RFU)) %>% 
  mutate(COLL_DATE = as.Date(COLL_DATE, "%m/%d/%Y")) 


field.data.chemonly <- file.path(root.dir, "data", "20191212_Chemistry_Only_2019.xlsx") %>% 
  readxl::read_excel(sheet = "Sheet1") %>% 
  mutate(Chl_ugL = as.numeric(Chl_ugL)) %>% 
  mutate(PC_ugL = as.numeric(PC_ugL)) %>% 
  mutate(Chl_RFU = as.numeric(Chl_RFU)) %>% 
  mutate(PC_RFU = as.numeric(PC_RFU)) %>% 
  mutate(COLL_DATE = as.Date(COLL_DATE, "%m/%d/%Y"))  

### Gather chem lab data to match the following:

# > table(field.data.macro$PROJECT)
# 
#         OTHER           RAS      RIBS_Scr         RMN             Special_Study               WALLKILL 
#             1            24       124             1               3                           3 
##          (habitat)                               (this is RSC)   (1 Patroons, 2 FL tribs)        

# > table(field.data.chemonly$PROJECT)
# 
#        Mohawk         OTHER           RAS              RIBS_Scr Special_Study      WALLKILL 
#            23             1            64                   3             8            40 
##                      09-INDN-2.0 (Alene, Matt K..?)

# Project names:
# Screenings, Fl tribs, Patroons, Halfway Cr, Birch Cr., Black Cr., Mohawk projects (incl 7/31 multiplate), Wallkill, habitat (only 2 samples?),


# Create simple, joined field data table

field.macro.simple <- field.data.macro %>% 
  select(SITE_ID, COLL_DATE, CREW, TEMP, PERCENT_SAT, DO, COND, SALINITY, PH, Chl_ugL, Chl_RFU, PC_ugL, PC_RFU, WATER_CHEM_COLLECT, CHEM_SAMP_LOC, EQUIP_USED, LANDUSE, W_DEPTH, W_WIDTH, CUR_SPD, CANOPY, ALGAE_D, ALGAE_S, ALGAE_FIL, BOTTOM_TYPE, DOM_SUBSTRATE, )

field.chemonly.simple <- field.data.chemonly %>% 
  select(SITE_ID, COLL_DATE, CREW, TEMP, PERCENT_SAT, DO, COND, SALINITY, PH, Chl_ugL, Chl_RFU, PC_ugL, PC_RFU, WATER_CHEM_COLLECT, CHEM_SAMP_LOC, EQUIP_USED, LANDUSE, W_DEPTH, W_WIDTH, CUR_SPD, CANOPY, ALGAE_D, ALGAE_S, ALGAE_FIL, BOTTOM_TYPE, DOM_SUBSTRATE, )

field.all <- bind_rows(field.macro.simple, field.chemonly.simple) %>% 
  mutate(EVENT_ID = paste0(SITE_ID,"_",as.character(COLL_DATE))) %>% 
  select(EVENT_ID, everything()) %>% 
  mutate(W_DEPTH = as.numeric(W_DEPTH)) %>% 
  mutate(W_WIDTH = as.numeric(W_WIDTH)) %>% 
  mutate(CUR_SPD = as.numeric(CUR_SPD)) %>% 
  mutate(CANOPY = as.numeric(CANOPY)) %>% 
  mutate(ALGAE_D = as.numeric(ALGAE_D)) %>% 
  na_if(-9999) %>% 
  na_if(-5)

# Look for duplicate event IDs
field.all.dups <- field.all %>% 
  group_by(EVENT_ID) %>% 
  filter(n()>1)

rm(field.data.macro, field.macro.simple, field.data.chemonly, field.chemonly.simple)

```

Load in lab data, subset, and join project names
```{r}
lab.data <- file.path(root.dir, "data", "2019_chlorophyll_pull_chem_qaqcd_2020-02-25.csv") %>% 
  read_csv() %>% 
  # select(SiteID, DEC_sample_type, sample_name, sample_source, sample_date, sample_delivery_group, sample_receipt_date, analysis_date, prep_date, chemical_name, result_value, result_unit, lab_qualifiers, method_detection_limit, reporting_detection_limit, quantitation_limit, detection_limit_unit) %>% 
  filter(chemical_name == "Chlorophyll A") %>% 
  mutate(sample_date2 = as.Date(sample_date, "%Y-%m-%d")) %>% 
  mutate(EVENT_ID = paste0(SiteID,"_",as.character(sample_date2))) %>% 
  rename(SDG = sample_delivery_group)

# Replace nondetect result_values with quanitatiation limits (no MDLs for chl...?)
lab.data$result_value <- ifelse(is.na(lab.data$result_value), lab.data$quantitation_limit, lab.data$result_value)

# Check for duplicate event IDs
lab.dups <- lab.data %>% 
  group_by(EVENT_ID) %>% 
  filter(n()>1)

# Import ALS project list for joining project names by SDG
project.names <- file.path(root.dir, "data", "ALS_project_list_NYSDEC 2019_2019-12-04.xlsx") %>%
  readxl::read_excel(sheet = "Streams only") %>%
  select(SDG, Project) %>% 
  mutate(Project = as.factor(Project))

lab.data <- left_join(lab.data, project.names, by = "SDG")

rm(lab.dups, project.names)

```

Join field and lab data
```{r}
lab.field.join <- full_join(field.all, lab.data, by = "EVENT_ID")

#Check for missing lab data
missing.fielddata <- lab.field.join %>% 
  filter(is.na(SITE_ID)) %>% 
  select(EVENT_ID, SiteID, sys_sample_code, chemical_name, sample_date, fraction, result_value, result_unit, validator_qualifiers, interpreted_qualifiers)

# write.csv(missing.fielddata, "missing_fielddata.csv", row.names = FALSE)

#Check for missing field data
missing.labdata <- lab.field.join %>% 
  filter(is.na(sys_sample_code)) %>% 
  select(EVENT_ID, SiteID, sys_sample_code, chemical_name, sample_date, fraction, result_value, result_unit, validator_qualifiers, interpreted_qualifiers)


#Filter down to sites where both ProDSS and lab data are present
lab.field.join <- lab.field.join %>% 
  filter(!is.na(Chl_ugL)) %>%
  filter(Chl_ugL != -9999) %>%
  filter(Chl_ugL != -5) %>% 
  filter(!is.na(sys_sample_code))

# 277 records, 191 unique sites present in above.
  
# lab.field.join.export <- lab.field.join %>% 
#   select(EVENT_ID, Chl_ugL, result_value)

# write.csv(lab.field.join, "chl_prodss_datajoin.csv", row.names = FALSE)

rm(field.all, field.all.dups, missing.fielddata, missing.labdata)

```

Filter data manually, and by outliers and extremes
```{r}
lab.field.join2 <- lab.field.join %>% 
  filter(EVENT_ID != "09-HAMM-1.9_2019-08-27") %>% 
  filter(EVENT_ID != "09-FSCR-9.2_2019-09-11") %>% 
  filter(EVENT_ID != "09-BLAH-4.2_2019-08-27")
  
# Using methods outlined here: https://www.r-bloggers.com/how-to-remove-outliers-in-r/

library(ggstatsplot)

quantile.lab <- quantile(lab.field.join$result_value, probs=c(.25, .75), na.rm = TRUE)
iqr.lab <- IQR(lab.field.join$result_value, na.rm = TRUE)
# up.lab.outlier <-  quantile.lab[2]+1.5*iqr.lab # Upper Range  
# low.lab.outlier <- quantile.lab[1]-1.5*iqr.lab # Lower Range
# up.lab.extreme <-  quantile.lab[2]+3*iqr.lab # Upper Range  
# low.lab.extreme <- quantile.lab[1]-3*iqr.lab # Lower Range


quantile.field <- quantile(lab.field.join$Chl_ugL, probs=c(.25, .75), na.rm = TRUE)
iqr.field <- IQR(lab.field.join$Chl_ugL, na.rm = TRUE)
# up.field.outlier <-  quantile.field[2]+1.5*iqr.field # Upper Range  
# low.field.outlier <- quantile.field[1]-1.5*iqr.field # Lower Range
# up.field.extreme <-  quantile.field[2]+3*iqr.field # Upper Range  
# low.field.extreme <- quantile.field[1]-3*iqr.field # Lower Range

lab.field.join.nooutliers <- lab.field.join %>% 
  subset(result_value > (quantile.lab[1] - 1.5*iqr.lab) & result_value < (quantile.lab[2]+1.5*iqr.lab)) %>%
  subset(Chl_ugL > (quantile.field[1] - 1.5*iqr.field) & Chl_ugL < (quantile.field[2]+1.5*iqr.field))

lab.field.join.noextremes <- lab.field.join %>% 
  subset(result_value > (quantile.lab[1] - 3*iqr.lab) & result_value < (quantile.lab[2]+3*iqr.lab)) %>%
  subset(Chl_ugL > (quantile.field[1] - 3*iqr.field) & Chl_ugL < (quantile.field[2]+3*iqr.field))

```

Base plot function
```{r}
# plot.all <- function(param, title, ylabel){
#   ggplot()+
#   geom_point(data = lab.field.join, aes(x = Chl_ugL, y = result_value)) +
#   # scale_color_manual(values = c("baseline" = "blue", "event" = "orange", "not observed" = "black")) +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=0.5)) +
#   ggtitle(title) +
#   xlab("Site ID") +
#   ylab(ylabel) +
#   guides(color=guide_legend(override.aes=list(shape=15, size = 5)))+
#   theme(legend.key=element_blank())
# }
```


# Plot all (outliers, no outliers, no extremes) 

```{r}

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, color = "blue", aes()) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI TA Sensor vs Lab-extracted Chl-a (all data)")

ggplot(data = lab.field.join, aes(x = Chl_RFU, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, color = "blue", aes()) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl RFU") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI TA Sensor RFU vs Lab-extracted Chl-a (all data)")

ggplot(data = lab.field.join2, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, color = "blue", aes()) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI Total Algae Sensor vs Lab-extracted Chl-a (filtered)") +
  theme_bw()

ggplot(data = lab.field.join2, aes(x = Chl_RFU, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, color = "blue", aes()) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl RFU") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI Total Algae Sensor RFU vs Lab-extracted Chl-a (filtered)") +
  theme_bw()

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, color = "blue", aes()) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI TA Sensor vs Lab-extracted Chl-a (extremes removed)")

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI TA Sensor vs Lab-extracted Chl-a (all data)")

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI TA Sensor vs Lab-extracted Chl-a (extremes removed)")

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  ggtitle("YSI TA Sensor vs Lab-extracted Chl-a (outliers removed)")

ggsave(filename = "alldata.png", width = 7, height = 4, units = "in", path = file.path(root.dir, "plots"))


```


# Plot by collection method

```{r echo = FALSE, fig.width=12, fig.height=4}

# Filter data to remove NAs and Pail samples
lab.field.join.equip <- lab.field.join %>% 
  filter(EQUIP_USED != "Pail") %>% 
  filter(!is.na(EQUIP_USED))

lab.field.join2.equip <- lab.field.join2 %>% 
  filter(EQUIP_USED != "Pail") %>% 
  filter(!is.na(EQUIP_USED))

lab.field.join.noextremes.equip <- lab.field.join.noextremes %>% 
  filter(EQUIP_USED != "Pail") %>% 
  filter(!is.na(EQUIP_USED))

lab.field.join.nooutliers.equip <- lab.field.join.nooutliers %>% 
  filter(EQUIP_USED != "Pail") %>% 
  filter(!is.na(EQUIP_USED))

# All data
ggplot(data = lab.field.join.equip, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = EQUIP_USED), show.legend = FALSE) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~EQUIP_USED, ncol = 5, scales = "fixed")

# Filtered
ggplot(data = lab.field.join2.equip, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = EQUIP_USED), show.legend = FALSE) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~EQUIP_USED, ncol = 5, scales = "fixed") +
  theme_bw()

# Extremes removed
ggplot(data = lab.field.join.noextremes.equip, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = EQUIP_USED), show.legend = FALSE) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~EQUIP_USED, ncol = 5, scales = "fixed")

#Outliers removed
ggplot(data = lab.field.join.nooutliers.equip, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = EQUIP_USED)) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~EQUIP_USED, ncol = 5, scales = "fixed")

lab.field.join.depthint <- lab.field.join %>% 
  filter(EQUIP_USED == "Depth_Integrated")

# ggsave(filename = "equip.png", width = 10, height = 3, units = "in", path = file.path(root.dir, "plots"))
```


# Plot by project

```{r echo = FALSE, fig.width=13, fig.height=6}

# filter out certain projects
lab.field.join2.proj <- lab.field.join2 %>% 
  filter(Project != "Birch Cr RAS") %>% 
  filter(Project != "Patroons Cr RAS")


ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project), show.legend = FALSE) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~Project, ncol = 5, scales = "fixed") 

ggplot(data = lab.field.join2.proj, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project), show.legend = FALSE) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~Project, ncol = 4, scales = "free")

ggplot(data = lab.field.join2.proj, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project), show.legend = FALSE) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~Project, ncol = 4, scales = "fixed") +
  scale_x_continuous(limits = c(-1, 30)) +
  scale_y_continuous(limits = c(0, 30)) +
  theme_bw()

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project), show.legend = FALSE) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~Project, ncol = 5, scales = "fixed") 
  # scale_x_continuous(limits = c(0, 8)) +
  # scale_y_continuous(limits = c(0, 8))

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = Project)) +
  # scale_color_manual(values=as.vector(alphabet2(11))) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~Project, ncol = 5, scales = "fixed") 

# ggsave(filename = "proj.png", width = 10, height = 5, units = "in", path = file.path(root.dir, "plots"))


```


# Plot by dom land use

```{r echo = FALSE, fig.width=12, fig.height=6}

# Subset data

# lab.field.join.landuse <- lab.field.join %>% 
#   filter(!is.na(LANDUSE))
lab.field.join2.landuse <- lab.field.join2 %>%
  filter(LANDUSE != "Industrial") %>% 
  filter(!is.na(LANDUSE))
  
# lab.field.join.noextremes.landuse <- lab.field.join.noextremes %>% 
#   filter(!is.na(LANDUSE))
# lab.field.join.nooutliers.landuse <- lab.field.join.nooutliers %>% 
#   filter(!is.na(LANDUSE))

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = LANDUSE)) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~LANDUSE, ncol = 5, scales = "fixed") 

ggplot(data = lab.field.join2.landuse, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = LANDUSE), show.legend = FALSE) +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~LANDUSE, ncol = 3, scales = "fixed") +
  # scale_x_continuous(limits = c(0, 10)) +
  scale_y_continuous(limits = c(0, 30)) +
  theme_bw()

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = LANDUSE)) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~LANDUSE, ncol = 5, scales = "fixed") + 
  # scale_x_continuous(limits = c(0, 12))
  scale_y_continuous(limits = c(0, 10))

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = LANDUSE)) +
  # scale_color_manual(values=as.vector(alphabet2(11))) +
  geom_smooth(method=lm) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~LANDUSE, ncol = 5, scales = "fixed") 
  # scale_x_continuous(limits = c(0, 6)) +
  # scale_y_continuous(limits = c(0, 6))


ggsave(filename = "landuse.png", width = 7, height = 4, units = "in", path = file.path(root.dir, "plots"))

```


Plot by stream width

```{r echo = FALSE, fig.width=12, fig.height=6}

# subset to where width data exists

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = W_WIDTH)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = W_WIDTH)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = W_WIDTH)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 


# ggsave(filename = "Wallkill_field_temp.png", width = 10, height = 6, units = "in", path = file.path(root.dir, "data/Wallkill_2018/plots"))

```

Plot by current spd
```{r echo = FALSE, fig.width=12, fig.height=6}

# subset to where width data exists

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = CUR_SPD)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = CUR_SPD)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = CUR_SPD)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 


# ggsave(filename = "Wallkill_field_temp.png", width = 10, height = 6, units = "in", path = file.path(root.dir, "data/Wallkill_2018/plots"))

```

Plot by depth 
```{r echo = FALSE, fig.width=12, fig.height=6}

# subset to where width data exists

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = W_DEPTH)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = W_DEPTH)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = W_DEPTH)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 


# ggsave(filename = "Wallkill_field_temp.png", width = 10, height = 6, units = "in", path = file.path(root.dir, "data/Wallkill_2018/plots"))

```


Plot by canopy cover
```{r echo = FALSE, fig.width=12, fig.height=6}

# subset to where width data exists

lab.field.join.bins <- lab.field.join %>%
  mutate(canopy_cat = case_when(
    CANOPY > 0 & CANOPY < 25 ~ "0-25%",
    CANOPY >= 25  & CANOPY < 50 ~ "25-50%",
    CANOPY >= 50  & CANOPY < 75 ~ "50-75%",
    CANOPY >= 75  & CANOPY <= 100 ~ "75-100%",
    TRUE ~ "BLANK"
  ))

lab.field.join2.bins <- lab.field.join2 %>%
  mutate(canopy_cat = case_when(
    CANOPY > 0 & CANOPY < 25 ~ "0-25%",
    CANOPY >= 25  & CANOPY < 50 ~ "25-50%",
    CANOPY >= 50  & CANOPY < 75 ~ "50-75%",
    CANOPY >= 75  & CANOPY <= 100 ~ "75-100%",
    TRUE ~ "BLANK"
  ))

lab.field.join.noextremes.bins <- lab.field.join.noextremes %>%
  mutate(canopy_cat = case_when(
    CANOPY > 0 & CANOPY < 25 ~ "0-25%",
    CANOPY >= 25  & CANOPY < 50 ~ "25-50%",
    CANOPY >= 50  & CANOPY < 75 ~ "50-75%",
    CANOPY >= 75  & CANOPY <= 100 ~ "75-100%",
    TRUE ~ "BLANK"
  ))

ggplot(data = lab.field.join, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = CANOPY)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 

ggplot(data = lab.field.join.bins, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = canopy_cat)) +
  # scale_color_gradient(low = "blue", high = "red") +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~canopy_cat, ncol = 5, scales = "free") +
  theme_bw() 
  # scale_x_continuous(limits = c(0, 30)) +
  # scale_y_continuous(limits = c(0, 30))

ggplot(data = lab.field.join2.bins, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = canopy_cat)) +
  # scale_color_gradient(low = "blue", high = "red") +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~canopy_cat, ncol = 4, scales = "fixed") +
  theme_bw() 
  # scale_x_continuous(limits = c(0, 30)) +
  # scale_y_continuous(limits = c(0, 30))

ggplot(data = lab.field.join.noextremes, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = CANOPY)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  theme_bw()

ggplot(data = lab.field.join.noextremes.bins, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = canopy_cat)) +
  # scale_color_gradient(low = "blue", high = "red") +
  geom_smooth(method=lm, formula = y ~ x) +
  stat_poly_eq(formula = y ~ x, aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), parse = TRUE) +
  geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") +
  facet_wrap(~canopy_cat, ncol = 5, scales = "fixed") +
  theme_bw()

ggplot(data = lab.field.join.nooutliers, aes(x = Chl_ugL, y = result_value), size = 3) +
  geom_point(shape = 19, size = 2, aes(color = CANOPY)) +
  scale_color_gradient(low = "blue", high = "red") +
  # geom_smooth(method=lm) +
  # geom_abline(aes(intercept=0, slope=1)) +
  xlab("YSI TA Chl ug/L") +
  ylab("Extracted chl ug/L") 


# ggsave(filename = "Wallkill_field_temp.png", width = 10, height = 6, units = "in", path = file.path(root.dir, "data/Wallkill_2018/plots"))

```


Join site info for exporting coords for AGOL map
```{r}

sites.table <- file.path(root.dir, "data", "20191224_Site_Field_cleaned_final.xlsx") %>% 
  readxl::read_excel(sheet = "Sheet1") %>% 
  rename(SITE_ID = BAS_LOC_RM)


chl.sites <- lab.field.join2 %>% 
  select(SITE_ID, Project) %>% 
  unique() %>% 
  left_join(sites.table, by = "SITE_ID") %>% 
  select(SITE_ID, SH_LATITUDE, SH_LONGITUDE, Project)

# write.csv(chl.sites, "chl_sites.csv", row.names = FALSE)

```

# Next steps:

# Create equation, R^2
# How to numberically compare 1:1 line and linear regression (or just data itself)
# plot individual screening trips by crew (color scale)?
# river size/width, other included params?
# Add in UFI fluoroprobe data (blue-green algae), compare to PC data.

